Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-09-11 Manuscript/manuscript.tex
Removed TODOs
Improved figure with the probability histogram of lipid-Na/Ca complexes.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.eps}
  \caption{\label{OrderParameterCHANGESsurf}
    Headgroup order parameter changes and P-N vector orientation as a function of
    cationic surfactant (dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$)
    in PC bilayer from simulations and experiments \cite{scherer89}.
  }
  \todo{Labels are missing.} \\
  \todo{Order should be the same as in other figures, i.e, $\beta$ segment on top.} \\
  \todo{I would put x-axis from 0 to 51 and maybe zoom y-axis little bit as well.}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/number_bound_lipids_p_cation_Ecc-lipids.eps} \\
  \caption{\label{fig:cacl_complexes}
      Histogram of relative probabilities of existence of complexes
      of \ce{Ca^{2+}} and $n$ POPC lipids. 
  }
  \todo{Change this figure so that it contains the relative probabilities of finding the particular clusters.}
\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.eps}
  \caption{\label{OrderParameterCHANGESsurf}
    Headgroup order parameter changes and P-N vector orientation as a function of
    cationic surfactant (dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$)
    in PC bilayer from simulations and experiments \cite{scherer89}.
  }
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/ipython_nb/stoichiometry_NaCl-CaCl2_comparison_Ecc-lipids.pdf} \\
  \caption{\label{fig:cacl_complexes}
      Relative probabilities of existence of \ce{Na^{+}} or \ce{Ca^{2+}} complexes
      with a certain number of POPC lipids. 
      \ce{Na^{+}} complexes were evaluated from the simulation with 1~M concentration;
      and \ce{Ca^{2+}} complexes were evaluated from the simulation with 287~mM concentration.
  }
\end{figure}
